%Senior Thesis Draft
%Ben Cook '14 (bacook@)
%Adviser: Neta Bahcall

\documentclass{puthesis_undergraduate}
%preamble
\input{thesis_setup}

\title{Keep Calm and Baryon: The Distribution of Baryons and Dark Matter on
  Cosmic Scales}
\author{Benjamin A. Cook}
\advisor{Prof. Neta Bahcall}

\abstract{How are baryons distributed in the universe? Where, and in
  what abundances, are they located in large, virialized systems such
  as galaxies, groups, and clusters? Here we determine the
  distribution of baryons, relative to dark matter, in systems ranging
  in size from galaxies to groups, clusters, and large-scale
  structure. We use observed X-ray and SZ measurements of the hot
  intracluster medium (ICM) to determine the hot gas contribution in
  groups and clusters; weak lensing and optical constraints on the
  cluster stellar fraction; and absorption measurements of the cool
  circumgalactic medium (CGM) to determine the gas mass in
  galaxies. Using direct observations when possible, and
  extrapolations of observed density profiles when necessary, we show
  that the baryon content within the virial radius is consistent with
  the cosmic baryon fraction ($0.164\pm0.004$) for systems ranging
  over three orders of magnitude in mass, from galaxies to groups and
  massive clusters. The baryon distribution is less extended in
  massive systems and more broadly distributed in low-mass
  systems. Averaged on scales larger than the virial radius, the
  baryonic mass is a strong tracer of the underlying dark matter
  distribution, and can be useful as a tool in cosmological studies of
  structure formation.}
  %Using the ratio of stellar fractions in galaxies and
  %clusters, we place a lower limit of $40\%$ on the contributions of
  %individual galaxy halos to the dark matter and baryonic mass of
  %clusters.}

\acknowledgements{First and foremost, I would like to thank Neta
  Bahcall for her wonderful support and guidance throughout this
  project, my graduate application process, and my entire Princeton
  career. She is an inspiration and invaluable mentor to every student
  in astrophysics and made me feel welcome in the department from my
  first day on campus. I'm very glad to have gotten the chance to
  conclude my senior year by working with her on this project, and I
  look forward to collaborating more on it in the future. I would
  like to thank Professor J.~Xavier Prochaska, Professor Lars
  Hernquist, and Dr.~Shy Genel for their discussions and insight into
  their work. I would also like to thank Dr.~Renyue Cen for making his
  simulations available for my analysis, which I regret I was not able
  to include in this thesis. Thank you to Tomer, Michael, Fred,
  and all the astro undergrads for the great times studying and
  working together in Peyton. Thank you to Shelby for believing in
  me, for giving me a reason to try harder and reach my full
  potential, and for always lifting my spirits when work is
  overwhelming. Finally, I would like to thank my parents, Kelly
  and Tom, for their love and encouragement and for giving me the
  opportunity to make it where I am today.}

\dedication{Dedicated to my brother, Walter.\\I'm very proud of you, and know you will
  accomplish amazing things.\\Continue to challenge
  yourself, and I'll enjoy my headstart while it lasts.}


\begin{document}
%=====================================================================

\input{Chapters/ch1_intro}

%=====================================================================
\input{Chapters/ch2_data}

\input{Chapters/ch3_results}

\input{Chapters/ch4_discussion}
\input{Chapters/ch5_conclusions}

\footnotesize
\bibliography{Thesis}
\addcontentsline{toc}{chapter}{Bibliography}

\appendix

\end{document}
