%Senior Thesis - First Chapter
%Ben Cook '14 (bacook@)
%Adviser: Neta Bahcall

\chapter{Introduction}
\label{chap:Intro}
\section{The Cosmic Matter-Energy Components}
\label{sec:Intro.Components}
After the big bang, the energy content of the universe was distributed
in a diverse number of components. As the universe expanded and
cooled, the available energy settled down into the primary energy
components we observe today, including radiation (photons and
neutrinos), baryons (``ordinary'' matter, comprised of protons,
neutrons, and electrons), as well as the mysterious dark matter and
dark energy.

Energy did not populate these forms in equal proportions; the energy
densities of each component differed by many orders of magnitude,
initially, and their ratios changed continually throughout the
expansion history of the universe. Radiation density -- primarily the
photon density (\rhog), dominant in the earliest periods after the big
bang -- diluted quickly from the combination of expansionary volume
increase and Doppler redshifting. The matter density -- \rhom,
comprised of both baryons (\rhob) and cold dark matter (\rhoc) -- was
initially only a minuscule portion of the cosmic energy budget, but
eventually matter dominated the cosmic scene after expansion
``cooled'' the photon temperature significantly. Initially
insignificant relative to the energy content of the other components,
dark energy -- $\rho_\Lambda$, commonly thought to be a cosmological
constant $\Lambda$ -- retains a constant energy density while the
universe expands and became dominant at late times when \rhom{} had
decreased significantly. Each of these energy densities are often
scaled by the critical density required to stop cosmic expansion:
\begin{equation}
\rhocrit = \frac{3H^2}{8\pi{}G} \nonumber
\end{equation}
with $H$ the Hubble parameter and $G$ Newton's constant. The density of each component relative to the critical
density is expressed as $\Omega$. For example:
\begin{equation}
\frac{\rhob}{\rhocrit} = \omegab\;.  \nonumber
\end{equation}


\section{The Cosmic Baryon Fraction}
\label{sec:Intro.Baryons}
Baryons and dark matter, the two components of the total matter
density, have the same dependence on the expansionary scale factor
and redshift. Since the total matter density is just their sum, the
total matter density also scales identically:
\begin{align}
\rhoc \propto \rhob \propto \rhom & \propto a^{-3} \nonumber \\
& \propto (1+z)^{3}. \nonumber
\end{align}
Therefore, we see that the ratio of baryons to dark matter will remain
constant at its primordial level throughout the history of the
universe. A useful and commonly studied constant is the \textit{cosmic
  baryon fraction}, \fb, the fraction of all matter in baryonic form:
\begin{equation}
\fb = \frac{\rhob}{\rhob + \rhoc} = \frac{\rhob}{\rhom} =
\frac{\omegab}{\omegam}\;.
\end{equation}

The above argument, that the baryon fraction remains constant
throughout cosmic history, applies only in the homogeneous regime,
when there are no spatial variations in the overall mass density. If
inhomogeneities exist, self-interactions lead to the complicated
evolution of structure. While dark matter (by energy density)
dominates the gravitational collapse of inhomogeneities and drive the
growth of structure, it is obvious that the baryonic abundance plays
an incredibly important role in determining the makeup of our
universe. Dark matter interacts only through gravity, but baryons are
subject to electromagnetic forces, thermal emission, collisions, and
numerous other interactions collectively known as ``baryonic
physics''. Baryons are solely responsible for all non-gravitational
phenomena studied in physics and astrophysics: the formation of
galaxies, stars, and planets, supernovae, radiation, magnetism,
chemistry, and, eventually, life itself. 

These baryonic effects lead to a divergence between the baryonic and
dark matter distributions, and hence a variation in the local baryon
fraction. Although the local baryon fraction may vary hugely from
place to place, it is possible to estimate the cosmic baryon fraction
by averaging over a substantially large volume. By studying the baryon
fraction (and what forms the baryons take) we can learn about the
relative distributions of dark matter and baryons, and the
contributions of baryonic and gravitational physics to the formation
of structure.

The baryon and dark matter abundances were major factors in several
important physical processes in the early universe. Through observable
signatures of these processes, cosmologists have been able to place
powerful constraints on the cosmic baryon fraction at these early
times. Consistent with the literature, we will consider the baryon
fraction inferred from these methods to be the cosmic fraction against
which we will compare measurements from the local, highly
inhomogeneous universe.

One mechanism that constrains the baryonic abundance is big bang
nucleosynthesis (BBN), the process which generated the first light
elements beyond hydrogen\footnote{The discussion which follows is
  guided primarily by Chapter 3.2 of \citet{Weinberg2008}, a useful
  but relatively technical reference on the topic.}. In the first
seconds after the big bang, the only ordinary matter particles which
existed (and were stable) were protons ($p$), electrons ($e$),
neutrons ($n$), and deuterium ($d$). The high temperatures and densities of nucleons
allowed the conversion of protons and neutrons into more complex and
heavier nuclei, through processes such as:
\begin{align}
p + n &\rightarrow{} d + \gamma \nonumber \\
d + d &\rightarrow{} ^3\textrm{He} + n \nonumber \\
d +{} ^3\textrm{He} &\rightarrow{} ^4\textrm{He} + p\; .\nonumber
\end{align}
The BBN reactions began around 100 -- 200 seconds after the big bang
\citep{Weinberg2008}. The exact time when these reactions reached
thermal equilibrium depends weakly on the abundance of baryons,
$\omegab h^2$, where $\Ho = 100h~\kmsMpc$ defines $h$, an important
scaling factor\footnote{Uncertainties on the true expansion rate ($h$)
  translate into uncertainties on a number of observables such as
  matter abundances ($\Omega$) and halo properties (\Mass{} or
  \radius{}). Therefore, many derived properties in the literature are
  often given in terms of $h_{70} \equiv{} \Ho / 70~\kmsMpc$.}. After
the universe expanded and cooled sufficiently, these reactions fell
out of equilibrium, leaving the universe enriched with helium ($^4$He
and $^3$He) and trace amounts of elements such as deuterium and
lithium ($^7$Li). The higher $\omegab h^2$, the more complete the
transformation of $n$ and $d$ into helium. Therefore, the baryon
abundance strongly affects the resulting abundance of deuterium and
residual elements like lithium and $^3$He. Figure \ref{fig:Abundances}
shows the dependence of these primordial abundances on the cosmic
baryon abundance.

\input{Figures/Abundances}

The baryon abundance can be determined through observational
constraints of, for example, the deuterium abundance, which among the
byproducts of BBN depends most strongly on $\omegab h^2$. The
deuterium abundance has been inferred from variety of sources,
including from the Milky Way's ISM \citep{Linsky1993, Linsky1995},
absorption towards QSOs \citep{Tytler1996, Kirkman2003}, and even from
measurements of the composition of the Jovian atmosphere
\citep{Niemann1996}. All such methods have limitations, as deuterium
can be destroyed in stellar (and brown dwarf) cores, altering the
deuterium abundance slightly with time. \citet{Iocco2009} provides a
compilation of deuterium abundance measurements, placing a
constraint on the baryon abundance of $\omegab h^2 = 0.021 \pm
0.001$. Observed $^7$Li abundances are a factor of a few lower than
predicted from BBN, suggesting that there could be additional physics
responsible for destroying lithium \citep{Suzuki2000,
  Melendez2004}. This is known as the ``Lithium Problem,'' and is
still an unsolved problem in interpreting BBN.

A complementary method of inferring the baryon abundance at early
times is from measurements of the acoustic peaks in the Cosmic
Microwave Background (CMB) power spectrum. The CMB power spectrum
contains large peaks, representing correlations in the CMB on
particular scales. In the first few hundred thousand years after the
big bang, the temperature of the universe was high enough to keep
atoms fully ionized into separate nuclei and electrons. These charged
particles were strongly coupled to the local photon field through
electromagnetic interactions, so that the two components combined to
form what is called a photon-baryon fluid. This fluid bfell towards the
centers of gravitational wells created by dark matter. However, unlike
the non-interacting dark matter, the photon-baryon fluid's pressure
rose when its density rose, stopping its infall. The pressure build-up
forced the fluid back out of the well until its pressure dropped
enough to allow gravity to draw it back once again. These ongoing
fluctuations in the pressure and density of the fluid were frozen into
the CMB power spectrum as the acoustic peaks. This occurred when the
average temperature of the universe dropped sufficiently to allow
neutral atoms to form, and the CMB photons began streaming freely
through the universe\footnote{For an introductory discussion on the
  concept of acoustic peaks in the CMB, see Chapter 9 of
  \citet{Ryden2003}.}.

The baryon abundance at this early time had several effects on the
acoustic peaks in the CMB, as did the overall mass abundance ($\omegam
h^2$). Figure \ref{fig:CMB_Power} shows how changes in these
abundances are reflected in the acoustic peaks. The location of the
first peak (and all subsequent peaks) is determined by the sound speed
at the epoch of last scattering. This sound speed increases when
$\omegab h^2$ increases, although it is more sensitive to changes in $\omegam
h^2$, an increase of which results in a decrease in the sound speed
\citep[][ch.~9.8]{Mukhanov2005}. The relative heights of the acoustic
peaks is a further diagnostic of the baryon abundance. As seen in
Figure \ref{fig:CMB_Power}, odd-numbered peaks are higher than
even-numbered peaks in a universe with high $\omegab h^2$. This is
because an increase in the amount of massive baryons reduces the
frequency of acoustic oscillations
\citep[][ch.~8.7.3]{Dodelson2003}. Finally, the power spectrum
declines towards higher multipoles ($l$) due to a process known as
``Silk Damping''. This damping term is due to imperfections in the
photon-baryon coupling, and the characteristic damping scale is
influenced by $\omegab h^2$ \citep[][ch.~4.7]{Durrer2008}.

Through a combination of all the processes listed above, modern CMB
observations have been able to place strong constraints on both
$\omegab h^2$ and $\omegam h^2$. Two of the most noteworthy such
measurements come from the \textit{Wilkinson Microwave Anisotropy
  Probe} \citep[\WMAP{},][]{Bennett2003} and the \textit{Planck} Satellite
\citep{PlanckResultsI}. Different constraints are placed on these
parameters depending on what additional data\footnote{\Ho, BAO,
  polarization, etc.} is included in the analysis. We will take the
median value (from each paper) of parameters derived through these
various methods, and we use the systematic variance in the parameters as
the uncertainty, if it is larger than the statistical uncertainty
listed from the analysis.

From the 9-year data release of \WMAP{} \citep[\WMAP9,][]{Hinshaw2013},
we take values $\omegab h^2 = 0.02229 \pm 0.00035$ and $\omegac h^2 =
0.1138 \pm 0.0032$. From the results paper of \Planck{}
\citep{PlanckResultsXVI}, we take the values $\omegab h^2 = 0.022115
\pm 0.00025$ and $\omegac h^2 = 0.11957 \pm 0.0025$. These values
allow us to constrain the cosmic baryon fraction as:
\begin{align}
\fb &= \frac{\omegab h^2}{\omegab h^2 + \omegac h^2} \\
&=0.164 \pm 0.004 \,\,(\WMAP9) \nonumber\\
&= 0.156 \pm 0.003\,\,(\Planck) \nonumber\\ 
\intertext{The uncertainty on \fb{} comes from the propogation of
  uncertainties on $\omegab h^2$ and $\omegac h^2$:}
\Delta\fb &=
\sqrt{\left(\frac{\partial\fb}{\partial\omegab h^2}\right)^2\Delta(\omegab h^2)^2 
+ \left(\frac{\partial\fb}{\partial\omegac h^2}\right)^2\Delta(\omegac h^2)^2} \nonumber \\
&= \sqrt{\left(\frac{\omegac h^2 \Delta(\omegab h^2)}{(\omegab h^2 + \omegac h^2)^2}\right)^2
+ \left(\frac{\omegab h^2 \Delta(\omegac h^2)}{(\omegab h^2 + \omegac h^2)^2}\right)^2} \nonumber \\
&= \frac{1}{(\omegam h^2)^2}\sqrt{\left[\omegac h^2 \Delta(\omegab h^2)\right]^2
+ \left[\omegab h^2 \Delta(\omegac h^2)\right]^2} 
\end{align}

It is commonly discussed \citeeg{Spergel2013} that the \Planck{}
results yield \omegam{} significantly higher and \Ho{} significantly
lower than other previous measurements, including \WMAP{}. This results
in the lower value of \fb{} as derived from \Planck{}. Earlier
estimates \citep[e.g.,\WMAP5,][]{Dunkley2009} placed \fb{}
around 0.17, a canonical value which is often used in the
literature. Because of the issues surrounding the interpretation of
the Planck data, we will use the WMAP9 measurement of $\fb{}\sim0.164$
for our primary comparisons with low-redshift baryon fractions,
although we will attempt to also compare to the Planck constraints
whenever possible. One limitation of this work is the relative
uncertainty on the ``cosmic'' baryon fraction due to the
discrepancies in CMB observations. We hope that subsequent
analysis of the \WMAP/\Planck{} disagreements will solve this problem, one
way or another.

\input{Figures/CMB_Power}

\section{The Cluster Missing Baryon Problem}
\label{sec:Missing.Clusters}

Large \textit{galaxy clusters} represent the most massive dark matter
halos which have had adequate time to virialize since the big
bang. The richest clusters often contain hundreds of large galaxies,
while much smaller \textit{groups} may contain several to tens of
galaxies. The galaxies are bound to the gravitational well of the
combined mass of the cluster, which includes dark matter as well as
baryons. Some clusters show a steep pressure profile (and a flat
density profile) towards their centers, suggesting that they are
dynamically \textit{relaxed} and possess a \textit{cool core} (these
are known as CC clusters). Clusters with flattened central pressure
profiles (and cuspy density profiles) are \textit{unrelaxed} or
\textit{non-cool core} (NCC) clusters. Because they are the largest
bound objects in the universe, clusters offer one of the best ways of
measuring the baryon fraction at low-redshift: they have collapsed
from large volumes and therefore represent the largest samples of the
cosmic dark matter and baryon densities that are not in dramatic
dynamical evolution. Additionally, their extremely deep gravitational
potential wells are expected to prevent any significant fraction of
baryons from escaping the system through feedback effects, such as
winds, supernovae, or AGN activity.

The baryonic component of galaxy clusters is not primarily stored in
galaxies, but in a hot ($\textrm{kT} \gsim 1$ keV), diffuse gas known
as the \textit{Intracluster Medium} (ICM). The ICM can be detected
through the X-ray brehmsstrahlung emission of the ionized
plasma. X-ray telescopes such as \Chandra, \Rosat, \Suzaku, and \XMM{}
have been key in detecting the ICM and constraining its distribution
and total mass \citeeg{Vikhlinin2006,Eckert2012}. A complementary
method of detecting and measuring the intracluster gas is through the
thermal Sunyaev-Zeldovich effect \citep[SZ,][]{Sunyaev1972}, which
occurs when the energy spectrum of background CMB photons passing
through the cluster is altered, due to inverse-Compton scattering with
the charged particles in the plasma.

The stars of individual galaxies make up the remainder of the baryonic
mass in clusters. Stellar mass is often derived from the luminosity in
starlight, which is converted into mass using typical stellar mass to
light ratios derived for individual galaxies \citep{Bahcall2014}.

The total mass of clusters is derived through stacked weak-lensing
analysis, where the average distortion of background galaxies is
measured as a function of cluster-centric radius. These distortions
can be inverted to compute the distribution of mass in the cluster
which is responsible for the gravitational lensing distortions. Recent
weak-lensing analyses \citep{Mandelbaum2008, Sheldon2009a} yield
accurate constraints on the total mass of clusters, and show that the
distribution of mass is fit well by the Navarro-Frenk-White
profile \citep[NFW,][]{Navarro1996}, a prediction from N-body
simulations of cold dark matter.

Before addressing the overall masses and sizes of galaxy clusters, it
is crucial to outline the definitions for these scales we will use
throughout this paper. Because dark matter halos are believed to be
self-similar (scaling only by overall mass or central density) their
sizes are often given relative to fixed overdensities $\Delta$, the
location where the density of matter interior is a particular multiple of
the critical density of the universe. For example, $\Delta = 200$
equates to the region in a halo where
\begin{equation}
\rhom(<r) = \frac{3M(<r)}{4\pi{}r^3} = 200\times\rhocrit\;. \nonumber
\end{equation}
The mass and radius of a galaxy cluster is typically measured at a
characteristic overdensity. For example, many sources in the
literature list the cluster mass and radius as \Mfive{} and
\rfive{}, measured at an overdensity of $\Delta = 500$. As cluster
mass is clustered towards the center, $\Delta$ decreases towards
larger cluster-centric radii. The gravitational system virializes
around $\Delta = 100$ \citep{Eke1996}, so we take the characteristic
scales of clusters to be the virial (or halo) mass and radius,
\Mvir{} $ \equiv $ M$_{100}$ and \rvir{} $ \equiv $ r$_{100}$.

Through stacked weak lensing measurements, rich galaxy clusters have
been observed to have halo masses of $10^{14}\dash10^{15}~\Msun{}$
\citep{Mandelbaum2008}, and halo radii of around $1\dash3$ Mpc
\citep{Vikhlinin2006}. Lower-mass ``groups'' typically have masses
around $10^{13} \dash 10^{14}~\Msun{}$, and represent the intermediate
range between the most massive clusters and large galaxies. The
self-similarity of group and cluster halos results in a fairly
constant relation between masses or radii at various overdensities. For
example \citep{Rasheed2011}:
\begin{equation}
\rvir{} \approx 1.3\times{}\rtwo{} \approx
1.9\times{}\rfive{}.
\end{equation}
Using an approximate mass density profile of $\rhom \propto
\textrm{r}^{-2.5}$ in these outer cluster regions, we assume that the
total mass scales roughly as M $\propto \textrm{r}^{0.5}$, so that
\begin{equation}
\Mvir{} \approx 1.14\times{}\Mtwo{} \approx 1.38 \times{}\Mvir{}.
\end{equation}

Recent X-ray and SZ measurements have begun to illuminate the hot
intracluster plasma, allowing detailed study of these large reservoirs
of baryons in groups and clusters. X-ray surface brightness
observations, in particular, are able to directly measure the gas
density profile and therefore retrieve the mass. However, because
brehmsstrahlung emission declines with the square of the gas density,
accurate X-ray measurements have typically been limited to the inner
regions of halos. Early studies of this kind in clusters include
\citet[][with \textit{Chandra}]{Vikhlinin2006} and \citet[][with
  \textit{XMM-Newton}]{Arnaud2007}, while \citet{Sun2009} made similar
measurements of the hot gas in groups using
\textit{Chandra}. Measuring the gas mass fraction only out to
\rfive{}, these observations typically found $\fg{}(<\rfive{}) \lsim
10$--$12\%$, well below the cosmic baryon fraction, although with
large variance between clusters. Importantly, there is a clear trend
towards lower gas content in lower-mass halos: nearly all groups and
small clusters show gas fractions well below 10$\%{}$ at \rfive{}. The
stellar fraction in clusters has been observed to increase in smaller
halos \citep{Giodini2009, Bahcall2014}. However, stars make up only a
few percent of the total mass even in groups and the smallest
clusters, and represent $<2\%$ of the total mass budget within
\rfive{} in rich clusters. Between ICM gas and stellar mass, there is
not nearly enough to make up the total baryonic mass predicted from
the cosmic baryon fraction.

\include{Figures/Giodini_Missing}

These discrepancies have been termed the ``Missing Baryon Problem'',
because observations have not been able to account for the expected
abundance of baryons in galaxy clusters. The problem is more severe in
smaller clusters, likely because baryons are less strongly bound to
their shallow gravitational wells. Many attempts have been made to
find a solution to this problem through theoretical and computational
means. Possibly the most predominant such explanation is that
additional non-gravitational energy is injected into the cluster, such
as through shocks \citep{Takizawa1998}, preheating \citep{Bialek2001},
or a number of feedback mechanisms due to star formation or AGN
activity \citep{Metzler1994, McCarthy2007, Bode2009}. The net result
of these additional energy sources is to extend the distribution of
hot gas in the ICM, pushing more baryonic matter into the outskirts of
the clusters while leaving the central regions devoid of gas and
stars. These theories predict that more sensitive analysis of the
outskirts of groups and clusters ($\gsim$\rvir{}) should recover the
missing gas mass left unaccounted for by observations of only the
inner cluster regions. \citet{Rasheed2011} used extrapolations of
observed gas density profiles to \rvir{}, corroborating the hypothesis
that the missing gas mass is hidden in the cluster
outskirts. Alternative theories predict that the missing baryons could
be residing in additional phases, such as a cool diffuse gas phase,
that have yet to be identified observationally \citep{Afshordi2007,
  Bonamente2005}.

\section{The Galaxy-Halo Missing Baryon Problem}
\label{sec:Missing.Galaxies}

Galaxies form in dark matter halos of a range of sizes. Galaxies like
the Milky Way and Andromeda (near the high-end of the galaxy mass
range) are commonly referred to as L$^*$ galaxies, and typically
reside in halos with masses upwards of $10^{12}$ \Msun{}
\citep{Moster2010}. The virial radii of these systems are around 300
kpc \citep[][and refs.~therein]{Werk2014}. The baryonic components
which dominate the energy output in these halos (and are therefore the
easiest to detect through emission) include the stellar disks, the gas
and dust of the interstellar medium (ISM), and a hot, X-ray emitting
halo of gas. Yet the most recent estimates of stellar mass in L$^*$
galaxies \citep{Behroozi2010} find that the stellar component makes up
only $\approx5\%$ of the total mass, far less than anticipated if
galactic halos also contain the cosmic baryon fraction. Including the
cold ISM gas measured by HI surveys and the hot X-ray halo
\citep[][respectively]{Martin2010, Gupta2012} only increases the
estimated baryon fraction in galaxies to around $8\%$. Therefore a
similar ``Missing Baryon Problem'' is discussed in galactic halos
because the disk cannot make up the entire anticipated baryon mass.

Several models have been developed which attempt to solve this
``Galaxy-Halo Missing Baryon Problem,'' through, for example, gas
escaping galaxies through winds, jets, and outflows. Some theories
predict unseen components in the intergalactic medium (IGM) which act
as further reservoirs for baryons, but have yet to be accurately
measured. These intergalactic components include a highly-photoionized
Ly$\alpha$ forest \citep{Sargent1980, Cen1994} or the warm-hot
intergalactic medium \citep[WHIM][]{Cen1999, Dave1999}. If galactic
halos are indeed deficient of baryons, these IGM components must
contain a higher proportion of baryons than expected from their
disperse dark matter content.

Another reservoir for galactic baryons is a diffuse region of gas
within the galactic halo itself, known as the circumgalactic medium
\citep[CGM][]{Bahcall1969, Bergeron1985, Lanzetta1995}, which may
contain a large mass of baryons. Observational studies have begun to
probe the CGM in the last few years through studies of QSO or galactic
sightlines which pass through the CGM \citep{Steidel2010,
  Prochaska2011, Tumlinson2011, Werk2013}. When photons emitted by the
background quasar or galaxy pass through the CGM, the gas (not
energetic enough to be detected in emission) absorbs characteristic
spectral lines from the background spectrum, depending on the chemical
makeup of the gas. The most common lines observed in absorption come
from neutral hydrogen -- hydrogen being the dominant source of
baryonic mass in the universe. However, absorption from more
highly-ionized species, such as \ion{Ca}{ii} \citep{Zhu2013},
\ion{Mg}{ii}, \ion{Si}{ii}, \ion{C}{ii}, and \ion{O}{vi}
\citep{Tumlinson2011, Werk2014}, which are not significant
contributors to baryonic mass, can be used to characterize the
ionization state of the CGM gas. Knowledge of the ionization state can
constrain the total hydrogen mass, including both neutral \ion{H}{i}
gas and the ionized \ion{H}{ii}. The observed metal-line absorption in
QSO sightlines and the enrichment of the CGM also suggest that
feedback effects are substantial in gaplaxy halos: metals created in
the stellar disk are expelled into the outer regions of the halo, or
even lost altogether, by feedback winds of $\gsim 10^2$ \kms{}
\citep{D'Odorico1991, Chen2010, Oppenheimer2012, Booth2012}.

\section{Our Investigation - Where are the Baryons?}
\label{sec:investigation}

In this thesis, we examine the most up-to-date observations available
that can help solve the ``Missing Baryon Problem'', and which address
the overall distribution of baryons relative to dark
matter. Generally, we wish to consider the questions: where are the
baryons in dark matter halos of all sizes, how are they distributed,
and what forms are they in? 

Gas density profiles in clusters are observed to be shallower than the
dark matter (NFW) profile, suggesting that there should be large
reservoirs of baryons in the outskirts \citeeg{Rasheed2011}. We use
published SZ and X-ray observations of cluster outskirts -- along with
extrapolations of the inner density profiles when necessary -- to show
that clusters \textit{do contain the expected baryon fraction} in
their halos; the baryons are less centrally concentrated than the dark
matter, so that previous observations of only the centers of clusters
systematically missed the baryons.

Galaxy halos have significantly lower mass than cluster halos and
their binding potential is lower, making it easier to expel baryons
from the halo by feedback effects. Because of this, it is possible
that the ``Galaxy-Halo Missing Baryon Problem'' is a consequence of a
majority of baryons being removed from the halos altogether. However,
the new observations of the CGM allow modernized constraints of the
mass-content of the outer galactic halos. We study the distribution of
baryons in galaxies using published absorption measurements of the
CGM, and find they are consistent with the scenario that the
\textit{entire baryon fraction} can also be found within the virial
radii of galaxies: a large fraction of the baryons simply reside in
the hard-to-detect CGM.

Our investigation is organized as follows. In Chapter \ref{chap:Data},
we present the observations which constrain the baryonic mass within
galaxy, group, and cluster halos. We also discuss the ways in which we
extract predictions for the baryon fraction at the virial radius from
extrapolations of measurements in the central regions. In Chapter
\ref{chap:Results}, we show our results and compare the observed
baryon fraction in halos to the cosmic baryon fraction derived from
BBN and the CMB. We demonstrate that current evidence suggests that,
averaged over sufficiently large scales, halos contain baryons in
abundances consistent with the cosmic baryon fraction. This is
observed in halos of a wide range of sizes, from galaxies to groups
and clusters. In Chapter \ref{chap:Discussion}, we discuss the
observational limitations and potential biases of our findings,
compare them to simulations, and discuss the implications of our
results. In Chapter \ref{chap:Conclusions}, we present our conclusions
on the subject of the baryonic mass distribution, and highlight future
work that can be done to improve our findings.

Throughout this paper, we assume a cosmology of $\omegam = 0.3$,
$\omegal = 0.7$, $\Ho = 70\,\kmsMpc$ ($h = 0.7$). Subscripts typically
signify the value is evaluated within the indicated radius, such as
$\fgfive{} = \fg{}(<\rfive)$.

