%Senior Thesis Chapter 4
%Ben Cook '14 (bacook@)
%Adviser: Neta Bahcall
\chapter{Discussion}
\label{chap:Discussion}

\section{Limitations and Observational Biases}
\label{sec:Limitations}

Due to the sensitivity required to accurately measure the gas
mass and total mass in clusters, our methods have included several
assumptions (such as that the ICM is in hydrostatic equilibrium, and
that the gas density slope is approximately constant from
$\approx\rfive{} or \rtwo{}$ to beyond \rvir{}) which require
additional discussion. Here, we discuss theoretical and observational
constraints on the magnitude of possible biases which we introduce by
making these simplifications.

\subsection{Assumption of Hydrostatic Equilibrium in Calculating Total
Mass}
\label{sec:Limitations.HSE}
As was highlighted throughout Chapter \ref{chap:Data}, there are
several different ways to calculate the total mass of groups and
clusters. One key characteristic of a mass estimation method is
whether it relies on the assumption of hydrostatic equilibrium. The
so-called ``hydrostatic mass'' ($\Mass{}_{HSE}$) can be calculated by combining the gas
density profile with either the temperature or pressure profile, a
method ubiquitous in X-ray observations. Using mass-scaling relations
(such as the Y$_\textrm{SZ}$-\Mfive{} relation) may also be sensitive
to the assumption of HSE if the relation is calibrated against
hydrostatic masses. Masses which do not rely on the assumption of HSE
are primarily derived from gravitational lensing.

Hydrostatic masses could be systematically biased, relative to the
``true'' mass (usually assumed to be the lensing mass, $\Mass{}_{WL}$)
if there are significant sources of non-thermal pressure in the
ICM. Examples include kinetic bulk motions or magnetic
fields. Hydrostatic equilibrium assumes that the gravitational force
(the total mass) is offset by the pressure gradient, so assuming that
only the gas pressure contributes can lead to a bias in the inferred
mass.

The magnitude of the hydrostatic mass bias is of paramount importance
to precision cosmology. Cosmological parameters (such as \omegam{})
derived from \Planck{} cluster counts and hydrostatic mass estimates
disagree significantly from values derived directly from the CMB power
spectrum, but a large hydrostatic mass bias ($ b= 1-
\Mass{}_{HSE}/\Mass{}_{WL} \approx 0.3$) could relieve the
observational tension \citep{Gruen2013,VonderLinden2014,
  Israel2014}. Such a large bias on the total halo mass would also
dramatically affect the gas fraction derived using hydrostatic masses,
affecting its use as a cosmological probe
\citeeg{Grego2001,Ettori2009b}. As the majority of our \fg{}
measurements in clusters were measured relative to hydrostatic masses
(with the exception of \citet{Umetsu2009}), our results are likewise
sensitive to the hydrostatic bias.

Cosmological simulations are a major tool used to constrain this bias.
The mass of simulated clusters can be compared to mock X-ray
observations which assume hydrostatic equilibrium, determining the
bias factor as a function of mass and overdensity. Simulations nearly
unanimously indicate that the hydrostatic mass is biased low compared
to the true halo mass ($b>0$), a bias which increases towards the
outskirts of clusters or in unrelaxed clusters, where merger
disruptions and bulk flows become more significant. Different
simulations and physical prescriptions place the bias anywhere from
$5\%$ \citeeg{Lau2009,Meneghetti2010,Burns2010,Nelson2012} to $20\%$
\citeeg{Arnaud2007,Nagai2007,Battaglia2013}.

Observational constraints on the hydrostatic mass bias vary widely,
however. Some weak lensing measurements of clusters suggest that
hydrostatic X-ray or SZ masses are biased low by $10\%$
\citep{Andersson2011,High2012}, and others indicate this bias could be
as large as $20\dash30\%$
\citep{Arnaud2007,Ichikawa2013,VonderLinden2014}. Yet others find no
significant difference between weak lensing masses and hydrostatic
masses, with some hints that hydrostatic equilibrium assumptions may
even \textit{overestimate} the true mass in lower-mass clusters
\citep{Gruen2013, Israel2014}. Figure \ref{fig:Gruen}, from
\citet{Gruen2013}, shows the agreement in their measured weak lensing
and hydrostatic masses.

\input{Figures/Gruen_Mass}
\afterpage{\clearpage}

The issue of hydrostatic mass bias is far from solved. Due to the
inconsistent observational and simulated constraints, it is unclear
how large of a hydrostatic correction factor should be included in our
measurements of the gas fraction, or if one is even necessary. A bias
low in the hydrostatic mass would bias the gas fraction high, meaning
that groups and clusters are slightly more deficient of baryons than
we suggest. However, the shallow gas density slope suggests that, if
the gas fraction is actually lower than observed, then integrating
further beyond $\rvir$ should recover the expected gas fraction. Our
choice to avoid using a hydrostatic correction factor until this issue
is clarified is slightly justified by the fact that one of our samples
(U09) measures gas fraction against the weak lensing mass, and this
fraction agrees well with gas fraction derived from the HSE
assumption.

\subsection{Gas Clumping in Cluster Outskirts}
\label{sec:Limitations.Clumping}

The primary means of deriving the gas density profile of clusters is
from measurements of X-ray surface-brightness, which scales with the
square of electron density. Due to this $n^2$ dependence, clumpy and
overdense structures in the ICM will emit more than their share of
X-ray luminosity, biasing gas density measurements high. The magnitude
of this bias depends on the smoothness of the ICM gas distribution,
which can vary widely from cluster to cluster.

Simulations typically predict a clumping bias (overestimate of
$\Mass{}_{gas}$) of $\approx10\dash15\%$
\citep{Nagai2011,Battaglia2013}, which increases in unrelaxed clusters
and towards cluster outskirts, where recent interactions have a more
significant dynamical effect. This could explain the large differences
in measured gas fraction between CC and NCC clusters, although
observations suggest that the level of clumpiness is overestimated in
simulations, and that the average bias is below $10\%$
\citep{Eckert2013c}. The majority of our cluster samples (with the
exception of the PC13 sample) represent only relaxed (CC) clusters, so
we do not include a clumping bias factor in our analysis. We also note
that the P13 \citep{PlanckIntV} and U09 \citep{Umetsu2009} gas
fractions are derived from SZ measurements, which do not suffer from
this clumping bias, and agree well with our X-ray data sets.

\subsection{Extrapolation of the Density Profile Slope}
\label{sec:Limitations.Slope}
The choice to extrapolate the gas fraction to $1.2\rvir{}$ and then
stop is arbitrary. Between \rfive{} and \rtwo{}, observations disagree
whether the slope remains roughly constant \citep{Dai2010} or steepens
by roughly $10\%$ \citep{Ettori2009a}. Assuming the true evolution is
somewhere in between, the gas density slope should not change
appreciably relative to the total mass (NFW) profile, which steepens
by about $4\%$ within this range. Above \rtwo{} (where
$\alpha{}_{gas}$ is measured), few accurate measurements of the gas
density slope exist. Therefore, our simplified model that
$\alpha{}_{m}$ and $\alpha_{gas}$ remain constant beyond \rtwo{}
should roughly approximate the increase of \fg{} with radius.

It is expected that the slope will eventually asymptote to match the
total mass (NFW) profile \citep{Umetsu2009, Battaglia2013}, suggesting
that, at large radius, $\alpha_{gas}$ will steepen more quickly that
$\alpha_{m}$. The point at which this occurs is not well constrained,
but it will taper the growth of \fg{}, which should eventually reach a
constant value. \citet{PlanckIntV} finds that the gas fraction in
stacked \Planck{} clusters flattens out between $1$ and
$1.5\rvir{}$. We approximate this by extrapolating \fg{} as constant
above $1.2\rvir{}$. However, until temperature measurements beyond
\rfive{} improve, the true radius where the baryon fraction reaches a
maximum will remain uncertain.

\section{Comparison to Simulations}
\label{sec:Simulations}

As discussed above, cosmological simulations have frequently been used
to examine the magnitude of observational biases on measurements of
cluster properties. Here we discuss the simulated cluster properties
themselves, from the simulations of \textbf{\citet{Battaglia2013}}. We
have discussed above that these simulations suggest that the
assumption of HSE may bias our observed gas and baryon fractions high,
and the true baryon fraction is lower by $\approx10\%$. Here, we
neglect these biases and compare the trends in their simulated gas and
baryon fraction to our observations, having concluded earlier that the
issue of mass bias is not yet settled.

The authors conducted a series of smoothed particle hydrodynamic (SPH)
simulations with three different physical feedback prescriptions: 1) a
``shock-heating'' only method, 2) a method that also included
radiative cooling and star formation/supernovae feedback, and 3) a
prescription including AGN thermal feedback. The simulations produced
(at $z=0$) a sample of over 1000 clusters with $\Mtwo >
7\power{13}~\Msun{}$, and 800 above $10^{14}~\Msun{}$.

\input{Figures/Battaglia_FbvM}

Figure \ref{fig:Battaglia_FbvM} shows the cumulative stellar, gas, and
baryon fractions in the simulated clusters, as a function of mass
(compare to our Figure \ref{fig:FgvM}). In the shock heating and
radiative cooling models, the total baryon fraction within
\rtwo{} is nearly the cosmic value in all clusters ranging from
$10^{14}\dash10^{15}~\Msun{}$. In the AGN feedback model, \fb{}
decreases in smaller halos, due primarily to suppressed stellar mass
production, although partly due to increased non-thermal
pressure pushing the gas towards higher radius. These simulations are
in agreement with our results that conclude the entire baryon
fraction can be recovered in clusters of all mass ranges when
accounting for cluster outskirts.

\input{Figures/Battaglia_FbvR}

Figure \ref{fig:Battaglia_FbvR} presents the radial distribution of
the gas, stellar, and baryon fractions for clusters binned by
mass. Only the results for the AGN feedback model are presented. The
stellar fraction decreases significantly from the center of the
clusters, with a higher stellar fraction in low-mass clusters for any
given radius. In all mass bins, however, the stellar fraction
asymptotically approaches a ``cosmic'' value of $\approx7\%$ (relative
to the baryon fraction). This behavior matches very well the stellar
fraction profile measured by \citet{Bahcall2014}, and the asymptotic
level of the simulated stellar fraction is in excellent agreement with
the observations ($6\%$ of the cosmic baryon
fraction).

The gas fraction profile also matches our observed trends well. The
gas fraction in the central regions of low mass clusters is
significantly lower but increases more rapidly with radius than in
high-mass clusters. The gas fraction in clusters of all mass converges
towards the same profile at high radius. Of particular interest,
however, is that even at $\radius{}>3\rtwo{}$ the gas fraction is
still increasing steadily. If this represents the gas profile in real
clusters (different feedback models have different behavior in the
outskirts), then our assumption that the gas fraction remains
constant above $1.2\rvir{}$ may need adjustment.

The overall baryon fraction increases from a minimum of $70-80\%$
cosmic within $0.5\rtwo{}$ to $>90\%$ outside the virial radius. The
fact that the baryon fraction does not reach the cosmic fraction until
very large radius ($>4\rtwo{}$) differs slightly from our results,but
this depends on the exact density profile being extrapolated.
Improved observations of the gas profile slope beyond \rtwo{} will
help constrain whether these simulations accurately predict how far
beyond the virial radius the baryons are extended. Additionally, the
simulations assume a cosmic baryon fraction of $\fb{} = 0.172$, higher
than current observational estimates. The increased baryon abundance
could lead to enhanced feedback effects, pushing baryons further from
the cluster centers than actually observed. Simulations which match
the current cosmological constraints would help clarify this issue.

\input{Figures/Battaglia_Fgvz}

Finally, in Figure \ref{fig:Battaglia_Fgvz}, we show the redshift
evolution in the gas fraction of the \citet{Battaglia2013} simulated
clusters. Measured from the cluster centers to far beyond the virial
radius, the gas fraction appears nearly constant with redshift at all
radii. Measured from $z=1.5-0$, this shows remarkable stability within
the ICM over many gigayears, including the phase when the most massive
clusters begin to form.

\section{Implications}
\label{sec:Implications}

Having addressed the possible observational biases in our measurements
and comparing our results to simulations, we address the global
conclusions about the distribution of baryons that our results allow
us to make. Understanding how baryons are distributed relative to dark
matter and what relative forms they take in different halos will
constrain how accurately baryons can be used as cosmological tools,
and how much the baryon fraction changes and evolves from early
cosmic times to today.

\subsection{Deviations from Self-Similarity}
\label{sec:Implications.Invariance}

Dark matter halos (both observationally and in simulations) are found
to fit the NFW density profile, and hence are, roughly,
``self-similar''. This means that all dark matter halos have the same
proportions and shapes, varying only by overall size. Assuming only
gravitational collapse, physical properties of baryons in clusters
(such as pressure and temperature) would be expected to obey
``universal profiles'', once scaled to the appropriate halo size
\citeeg{Arnaud2010,PlanckIntV}.

Although we have shown that the entire baryonic mass can be accounted
for in halos ranging over three orders of magnitude in mass, the
concentrations of gas and stellar fractions vary with halo mass. Pure
self-similarity would suggest that the baryon fraction should reach
the cosmic value at the same overdensity (such as $\rtwo$ or
$\radius{}_{100}$) regardless of halo mass. However, observations of
the gas fraction (Section \ref{sec:Spatial}) and the stellar fraction
\citep{Bahcall2014} in clusters indicate that the scale at which these
fractions asymptote to the cosmic values decreases with cluster
mass. Baryons in less massive halos are extended farther relative to
their virial radii than in massive clusters, an observation which is
supported by cosmological simulations \citep{Battaglia2013}.

Therefore, as expected, baryonic physics plays an important role in shaping the
distribution of baryons on scales smaller than the virial radius in
halos. Feedback effects (such as merger shocks, AGN feedback, and star
formation) are able to push baryons further into the outskirts of
small halos than in large halos, due to the decreased gravitational
potential. However, as our results indicate, these feedback effects
are not so powerful as to remove a substantial fraction of baryons
from the halos altogether, and nearly the entire baryon fraction
remains bound (or nearly bound) to dark matter halos.

\subsection{The Contribution of Individual Galaxies to Clusters}
\label{sec:Implications.Individual}

\citet{Bahcall2014} found that the overall mass-to-light ratio of
clusters matches closely the average mass-to-light ratio of individual
galaxies (plus the added gas content), when normalized by the changing
ratio of elliptical and spiral galaxies with cluster radius (the
``density-morphology relation''). This is consistent with the picture
that the entire dark matter content of groups, clusters, and
large-scale structure is comprised of the dark matter originally bound
to galaxy halos, which fell into the clusters and was stripped to form
the cluster halo. There is no reason, they argue, to assume that
groups and clusters contain more dark matter (relative to light) than
individual galaxy halos do \cite[unlike as previously believed by
  e.g.,][]{Ostriker1974, Guo2010}.

Our results further expand on this picture. The results described
above suggest that the entire mass content of groups, clusters, and
large-scale structure is comprised of the content of the infalling
galaxies: the dark matter, stars, and gas. Combining the stellar mass
of galaxies with observations of the multiphase CGM gas,
\citet{Werk2014} demonstrated that large, $\sim$L$^*$ galaxies contain
approximately the cosmic fraction of baryons within their $\approx300$
kpc halos, the same fraction observed within groups and clusters and
expected to extend beyond into the large-scale structure. Individual
$\sim$L$^*$ galaxies, falling into larger structures, may bring with
them most of the dark matter and baryons which make up the larger
systems. The consistency of the baryon fraction in galaxies and larger
structures suggests that groups, clusters, and large-scale structure
do not necessarily need a significant source of non-galactic
baryons to explain the high abundances in their halos: the
baryons could be comprised mostly of the baryonic mass once held in
the halos of constituent galaxies. The ICM, therefore, could be mostly
the stripped remains of galactic ISMs and CGMs, with the stellar disks
remaining mostly as cluster galaxies, with a small amount being
dispersed as the diffuse intracluster light (ICL).

Stars make up $15\%$ of the baryons within the virial radius of
$\sim$L$^*$ galaxies in the field, \citep{Werk2014}, in good agreement
with the $\approx15\%$ stellar fraction of baryons within \rvir{} of
groups \citep{Bahcall2014}. This agreement further suggests that the
total stellar mass of groups could be made up of the contribution of
individual L$^*$ galaxies which fell into groups. As the baryon
fraction of galaxies is also consistent with that of groups (within
the virial radius), most of the dark matter, gas, and stellar fraction
of groups could come from the constituent galaxies.

The baryon content of massive clusters, however, is made up of a
smaller fraction of stars, only $\approx6\%$ within \rvir. This may
suggest that galaxies only make up $\sim 6/15 = 40\%$ of the stellar
(and baryonic) mass of clusters, and additional (non-galactic) gas and
dark matter may have fallen into rich clusters to decrease the cluster
stellar fraction. Another possible solution is that galaxies which
fell into massive clusters did not form as many stars, with the hot
environment of the cluster quenching star formation in the constituent
galaxies. We also note that the average total mass of L$^*$ galaxies
assumed by \citet{Bahcall2014} ($\approx 3\power{12}~\Msun$) and
\citet{Werk2014} ($\approx1.6\power{12}~\Msun$) differ by a
non-negligible margin, and could explain the difference in their
stellar fractions. Further analysis is required to more accurately
measure the stellar fraction in L$^*$ galaxies, groups, and clusters,
but we appear close to being able to constrain the contribution of
galaxies to the total stellar and baryonic mass of groups and
clusters.

\subsection{Where are the Baryons?}
\label{sec:Implications.Where}

Our results show that the entire expected baryon content of dark
matter halos can be detected or inferred using current
observations. While the gaseous component of the baryons is more
extended than the dark matter, they are still bound to their host
halos, and there is no significant problem of baryons missing from
halos. Therefore, the answer to the question, ``Where are the baryons
in dark matter halos?'' is answered simply as: they are found in
the halos, distributed in various combinations between the central
regions and the diffuse outskirts.

The size and frequency of virialized halos define the overall
structure of matter in the universe. Because baryons populate in
nearly equal abundances galactic, group, and cluster halos, on large
scales they represent excellent tracers of the overall dark matter
distribution and structure. A relevant physical scale seems to be the
halo virial radius: this scale separates the regimes where baryons
do/do not trace the dark matter. On scales smaller than the virial
radius, baryons are under-abundant, relative to their cosmic fraction,
due to heating and other baryonic physics; this shortage is dependent
on the overall mass of the halo. However, averaging on scales larger
than \rvir{}, baryons match the dark matter distribution of the cosmos
at a nearly constant fraction.

During the earliest phases of structure formation baryons and dark
matter fell (in the cosmic fraction) into the newly forming
gravitational potentials. Whether baryons remained in these dark
matter halos at this cosmic fraction, or if baryonic physics expelled
a large fraction of the baryons from the system, has been unknown
until now. Our results suggest that virialized systems, from galaxies
to groups, clusters, and even large-scale structure, all retain
approximately the cosmic fraction of baryons. Heating and other
feedback effects have broadened the baryon distribution, so that
baryons are further extended into the outskirts of halos than dark
matter, but they remain in the expected cosmic fraction within the
potential. This picture further suggests, as originally proposed by
\citet{Bahcall2014}, that the makeup of groups, clusters, and
large-scale structure may be nearly entirely dominated by the
contributions of individual $\sim$L$^*$ galaxies: their dark matter
and baryons, gas, and stars.
